Adaptive broadcast tree for multicores

### 2013-06-04 graphs/visu_ziger_cluster.tex
Added forgotten file

\node at (0mm,360mm) {Machine: ziger, topology: binarytree};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (60mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (61mm,30mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (71mm,30mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (71mm,15mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (91mm,15mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (82mm,75mm) {};
\draw[->] (s_2_5.center) -- (r_2_5.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (92mm,75mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (102mm,75mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (92mm,60mm) {};
\draw[->] (s_1_4.center) -- (r_1_4.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (102mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (112mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
\draw[->,very thick,color=red] (s_2_6.center) -- (r_2_6.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_6_14) at (111mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (102mm,45mm) {};
\draw[->] (s_1_3.center) -- (r_1_3.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (112mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (122mm,45mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (112mm,165mm) {};
\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (122mm,165mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (122mm,150mm) {};
\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (132mm,150mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (142mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (131mm,210mm) {};
\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (132mm,135mm) {};
\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (142mm,135mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (152mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (132mm,180mm) {};
\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (132mm,120mm) {};
\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (142mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (152mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (141mm,195mm) {};
\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (142mm,105mm) {};
\draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (152mm,105mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (162mm,105mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (152mm,345mm) {};
\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (162mm,330mm) {};
\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (172mm,300mm) {};
\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (172mm,255mm) {};
\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (172mm,315mm) {};
\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (182mm,225mm) {};
\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (182mm,285mm) {};
\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center);

>>>>

\node at (0mm,360mm) {Machine: ziger, topology: cluster};
\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (70mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (80mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (90mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (100mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (110mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (70mm,270mm) {};
\draw[->,very thick,color=red] (s_0_18.center) -- (r_0_18.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_18_6) at (80mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_23) at (90mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_22) at (100mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_21) at (110mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_20) at (120mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_19) at (130mm,270mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (81mm,75mm) {};
\draw[->] (s_0_5.center) -- (r_0_5.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (90mm,180mm) {};
\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_17) at (100mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_16) at (110mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (120mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (130mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (91mm,60mm) {};
\draw[->] (s_0_4.center) -- (r_0_4.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (101mm,45mm) {};
\draw[->] (s_0_3.center) -- (r_0_3.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_23) at (101mm,345mm) {};
\draw[->] (s_18_23.center) -- (r_18_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_6) at (110mm,90mm) {};
\draw[->,very thick,color=red] (s_18_6.center) -- (r_18_6.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_6_11) at (120mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_10) at (130mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_9) at (140mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_8) at (150mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_7) at (160mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_17) at (111mm,255mm) {};
\draw[->] (s_12_17.center) -- (r_12_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (111mm,30mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_18_22) at (111mm,330mm) {};
\draw[->] (s_18_22.center) -- (r_18_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_16) at (121mm,240mm) {};
\draw[->] (s_12_16.center) -- (r_12_16.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (121mm,15mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_18_21) at (121mm,315mm) {};
\draw[->] (s_18_21.center) -- (r_18_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_6_11) at (131mm,165mm) {};
\draw[->] (s_6_11.center) -- (r_6_11.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_20) at (131mm,300mm) {};
\draw[->] (s_18_20.center) -- (r_18_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (131mm,225mm) {};
\draw[->] (s_12_15.center) -- (r_12_15.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_19) at (141mm,285mm) {};
\draw[->] (s_18_19.center) -- (r_18_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (141mm,210mm) {};
\draw[->] (s_12_14.center) -- (r_12_14.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_6_10) at (141mm,150mm) {};
\draw[->] (s_6_10.center) -- (r_6_10.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_6_9) at (151mm,135mm) {};
\draw[->] (s_6_9.center) -- (r_6_9.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};
\draw[->] (s_12_13.center) -- (r_12_13.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_6_8) at (161mm,120mm) {};
\draw[->] (s_6_8.center) -- (r_6_8.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_6_7) at (171mm,105mm) {};
\draw[->] (s_6_7.center) -- (r_6_7.center);

### 2013-06-04 graphs/visu_ziger_mst.tex
Added forgotten file

\node at (0mm,360mm) {Machine: ziger, topology: cluster};
\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (60mm,0mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (70mm,270mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_18_6) at (80mm,270mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (90mm,180mm) {};
\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_17) at (100mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_16) at (110mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (120mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (130mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};

@@

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_18_6) at (110mm,90mm) {};
\draw[->,very thick,color=red] (s_18_6.center) -- (r_18_6.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_6_11) at (120mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_10) at (130mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_9) at (140mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_8) at (150mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_7) at (160mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_17) at (111mm,255mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_16) at (121mm,240mm) {};

@@

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_6_11) at (131mm,165mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (131mm,225mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (141mm,210mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_6_10) at (141mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_9) at (151mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_6_8) at (161mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_7) at (171mm,105mm) {};

>>>>

\node at (0mm,360mm) {Machine: ziger, topology: mst};
\node[draw,fill=red!20,minimum size=10mm] (s_0_6) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (60mm,0mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_6) at (70mm,90mm) {};
\draw[->,very thick,color=red] (s_0_6.center) -- (r_0_6.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_6_12) at (80mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_11) at (90mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_10) at (100mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_9) at (110mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_8) at (120mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_7) at (130mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (80mm,270mm) {};

@@

@@

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_6_12) at (100mm,180mm) {};
\draw[->,very thick,color=red] (s_6_12.center) -- (r_6_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_17) at (110mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_16) at (120mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (130mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (140mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (150mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_11) at (101mm,165mm) {};

@@

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_6_10) at (111mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_6_9) at (121mm,135mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_17) at (121mm,255mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_6_8) at (131mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_16) at (131mm,240mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_6_7) at (141mm,105mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (141mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (151mm,210mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (161mm,195mm) {};

@@

### 2013-06-04 graphs/visu_ziger_sequential.tex
Added forgotten file

\node at (0mm,360mm) {Machine: ziger, topology: cluster};
\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (70mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (80mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (90mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (100mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (110mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (70mm,270mm) {};

@@

\node[draw,fill=red!20,minimum size=10mm] (s_18_6) at (80mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_23) at (90mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_22) at (100mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_21) at (110mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_20) at (120mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_19) at (130mm,270mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (81mm,75mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (90mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_17) at (100mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_16) at (110mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (120mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (130mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (91mm,60mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (101mm,45mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_18_23) at (101mm,345mm) {};
\draw[->] (s_18_23.center) -- (r_18_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_6) at (110mm,90mm) {};
\draw[->,very thick,color=red] (s_18_6.center) -- (r_18_6.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_6_11) at (120mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_10) at (130mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_9) at (140mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_8) at (150mm,90mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_6_7) at (160mm,90mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_17) at (111mm,255mm) {};
\draw[->] (s_12_17.center) -- (r_12_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (111mm,30mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_18_22) at (111mm,330mm) {};
\draw[->] (s_18_22.center) -- (r_18_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_16) at (121mm,240mm) {};
\draw[->] (s_12_16.center) -- (r_12_16.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (121mm,15mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_18_21) at (121mm,315mm) {};
\draw[->] (s_18_21.center) -- (r_18_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_6_11) at (131mm,165mm) {};
\draw[->] (s_6_11.center) -- (r_6_11.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_20) at (131mm,300mm) {};
\draw[->] (s_18_20.center) -- (r_18_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (131mm,225mm) {};
\draw[->] (s_12_15.center) -- (r_12_15.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_19) at (141mm,285mm) {};
\draw[->] (s_18_19.center) -- (r_18_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (141mm,210mm) {};
\draw[->] (s_12_14.center) -- (r_12_14.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_6_10) at (141mm,150mm) {};
\draw[->] (s_6_10.center) -- (r_6_10.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_6_9) at (151mm,135mm) {};
\draw[->] (s_6_9.center) -- (r_6_9.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};
\draw[->] (s_12_13.center) -- (r_12_13.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_6_8) at (161mm,120mm) {};
\draw[->] (s_6_8.center) -- (r_6_8.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_6_7) at (171mm,105mm) {};
\draw[->] (s_6_7.center) -- (r_6_7.center);

>>>>

\node at (0mm,360mm) {Machine: ziger, topology: sequential};
\node[draw,fill=red!20,minimum size=10mm] (s_0_17) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_15) at (70mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_14) at (80mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_13) at (90mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (100mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_23) at (110mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_22) at (120mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_21) at (130mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_20) at (140mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_19) at (150mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (160mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_11) at (170mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_10) at (180mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_9) at (190mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (200mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_7) at (210mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_6) at (220mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (230mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (240mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (250mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (260mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (270mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_17) at (80mm,255mm) {};
\draw[->,very thick,color=red] (s_0_17.center) -- (r_0_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (90mm,240mm) {};
\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_15) at (100mm,225mm) {};
\draw[->,very thick,color=red] (s_0_15.center) -- (r_0_15.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_14) at (110mm,210mm) {};
\draw[->,very thick,color=red] (s_0_14.center) -- (r_0_14.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_13) at (120mm,195mm) {};
\draw[->,very thick,color=red] (s_0_13.center) -- (r_0_13.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (130mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_23) at (130mm,345mm) {};
\draw[->,very thick,color=red] (s_0_23.center) -- (r_0_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_22) at (140mm,330mm) {};
\draw[->,very thick,color=red] (s_0_22.center) -- (r_0_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_21) at (150mm,315mm) {};
\draw[->,very thick,color=red] (s_0_21.center) -- (r_0_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_20) at (160mm,300mm) {};
\draw[->,very thick,color=red] (s_0_20.center) -- (r_0_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_19) at (170mm,285mm) {};
\draw[->,very thick,color=red] (s_0_19.center) -- (r_0_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (180mm,270mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_11) at (190mm,165mm) {};
\draw[->,very thick,color=red] (s_0_11.center) -- (r_0_11.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_10) at (200mm,150mm) {};
\draw[->,very thick,color=red] (s_0_10.center) -- (r_0_10.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_9) at (210mm,135mm) {};
\draw[->,very thick,color=red] (s_0_9.center) -- (r_0_9.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (220mm,120mm) {};
\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_7) at (230mm,105mm) {};
\draw[->,very thick,color=red] (s_0_7.center) -- (r_0_7.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_6) at (240mm,90mm) {};
\draw[->,very thick,color=red] (s_0_6.center) -- (r_0_6.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (241mm,75mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (251mm,60mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (261mm,45mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (271mm,30mm) {};

@@

\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (281mm,15mm) {};

@@
